Identifying Heterogeneity in SAR Data with New Test Statistics

### 2024-05-27 Text/Reviews/ResponsesR0R1-Reviewer1.tex

\medskip

%-------------------------------------
\begin{reviewbox}{Comment 1}
Page 2, line 81. When defining L, do you refer to the number of looks or to the equivalent number of looks?

\end{reviewbox}

\begin{responsebox}{Response}
We have clarified that
\begin{quote}
	\textcolor{blue}{\(L \geq 1\) is the number of looks (either nominal or estimated, thus not restricted to integer values),}
\end{quote}
\end{responsebox}

@@

\begin{reviewbox}{Comment 2}
Page 15, line 266. Could you please better define the intensity format? Does it refer to GRD? In that case, which acquisition mode and which final equivalent number of looks? How does this information relates with the L values in Figure 13 caption? It would also be useful to complement the description with the images acquisition date.
\end{reviewbox}

\begin{responsebox}{Response}

We have clarified the intensity format to refer to Ground Range Detected (GRD) data. Also, we have added Table 9 that provides a detailed overview of the SAR images selected.

We have clarified (line 264) that
\begin{quote}
	\textcolor{blue}{
	We evaluated the proposed test statistics using four SAR images: one of Rotterdam, 
Netherlands, acquired by the TerraSAR-X satellite with Single-look Slant-range Complex 
(SSC) and high-resolution Spotlight-mode (HS); another of the Coast of Jalisco, Mexico; and
two of Illinois, USA, acquired by the Sentinel-1B in Ground Range Detected (GRD) format, 
with ExtraWide-swath mode (EW) and Strip Map mode (SM). Table 9 provides detailed
parameters of the selected SAR images.
}
\end{quote}

@@

\end{responsebox}

\begin{reviewbox}{Comment 3}
Page 15, Figure 13. In order to ease the interpretation of the results for the 3 sites, it would be useful to show an optical image (the closest's Sentinel-2 available for example) of the corresponding SAR images.
\begin{responsebox}{Response}
 We have added the optical images obtained from Sentinel-2 for the corresponding SAR images. These optical images are now shown in Figure 14. This addition helps to facilitate the interpretation of the results and more clearly differentiate the homogeneous and heterogeneous regions.
\end{responsebox}
\end{reviewbox}
\begin{reviewbox}{Comment 4}
Page 15, Figure 13 caption. In reference to the L values 18, 36 and 36. Could you please provide more information about how you get those values?
\end{reviewbox}
\begin{responsebox}{Response}

In reference to the $L$ values 18, 36, and 36 in the caption of Figure 13, these values represent the number of looks used in our analysis.

We have clarified (line 271) that
\begin{quote}
	\textcolor{blue}{
The number of looks, $L$, was determined from the metadata in SNAP (Sentinel Application Platform), consisting of azimuth looks multiplied by range looks. This value also approximates the equivalent number of looks (ENL), calculated through the ratio of the squared sample mean to the sample variance in textureless areas.
}
\end{quote}

\begin{reviewbox}{Comment 5}
Page 16, line 269. Could you comment on why you selected a 7x7 window?
\end{reviewbox}
\begin{responsebox}{Response}

In SAR image processing, the selection of window size is crucial. Very large windows can average out local details, reducing sensitivity to fine-scale variations, while very small windows may not provide enough data for reliable statistical estimates. Our choice of a 7x7 window strikes a balance, capturing detailed local information while ensuring sufficient data points for robust analysis. Additionally, practical scenarios in SAR image processing often involve small sample sizes, typically obtained over windows of size 7x7.

We have clarified (line 280) that

\begin{quote}
	\textcolor{blue}{The three statistical tests are applied to the SAR images using 7 x 7 local sliding 
windows (This window size is commonly used in practical scenarios, which strikes a balance between capturing detailed local information and ensuring a sufficient number of data points to solid analysis)}
\end{quote}

@@

\end{responsebox}

\begin{reviewbox}{Comment 6}
As a suggestion, in order to conduct a more quantitative analysis of the results for each estimator, would you consider comparing the mean and standard deviation values of the different tests among some reference areas in the images? Ideally, a land cover map would serve. Alternatively, you may use some polygons with a clear land cover label (water, vegetation, urban). This would also serve to evaluate the sensitivity of the estimators for classification purposes.
\end{reviewbox}

\begin{reviewbox}{Comment 7}
Some general comments:
\begin{itemize}
	\item in the case you chose an GRD image. Wouldn't it make more sense to apply the operators on an Single Look Complex image so in native SAR coordinates?
	\item could you comment what to expect if doing the same tests employing higher resolution images such as TerraSAR-X's?
	\item could you comment what would be the impact of your work in classification applications with SAR images?
\end{itemize}
\end{reviewbox}

\begin{responsebox}{Response}
\begin{itemize}
 \item We chose to use GRD images for our analysis due to their preprocessing, which includes multilooking, making them suitable for statistical analysis over larger areas. While SLC images offer higher resolution, our focus on intensity-based heterogeneity detection is effectively addressed with GRD images. 
Future work could explore the application of our methods on SLC images to potentially leverage their higher resolution.
We focused on Sentinel-1B GRD images. Our results indicated that the Shannon entropy-based test performed better than the CV-based tests in detecting heterogeneity but with a higher number of looks.

\item In response to your comment, we extended our analysis to include a high-resolution TerraSAR-X image of Rotterdam, acquired in Spotlight mode with a single look and a resolution of 0.85x0.85 meters.
Our findings showed that the entropy test was less effective in detecting heterogeneity in this high-resolution single-look image compared to the Sentinel-1B images. 
The performance of the entropy test appears to be influenced significantly by the number of looks.
In contrast, for the TerraSAR-X image with a single look, the classical CV test was more effective in identifying heterogeneous regions.

\item Our work focuses on identifying heterogeneity in SAR images, which is a crucial aspect of image classification. 
The entropy-based test and coefficient of variation metrics we propose can improve the differentiation between homogeneous and heterogeneous areas, thus improving the accuracy of classification algorithms. 
By providing robust measures of heterogeneity, our methods can be integrated into classification workflows to better distinguish between different land cover types and detect subtle changes within classes. This could be especially beneficial in applications such as environmental monitoring and urban planning.
\end{itemize}

### 2024-05-27 Text/R1-Identifying Heterogeneity in SAR Data with New Test Statistics.Rmd
Updated paper with corrections

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   - \captionsetup[subfigure]{labelformat=parens, justification=centering}
   - \usepackage{placeins}

@@

@@

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=121$.", fig.width=6, fig.height=5}

@@

After checking the data's normality, we examined the proposed test's abilities in terms of size and power.
Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
Therefore, the \(p\) values are calculated as
\(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by:
\[
\varepsilon=\frac{\widetilde{H}_{\text{AO}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right]}{\widehat\sigma}.
\]

We have nominal levels of \SI{1}{\percent}, \SI{5}{\percent}, and
\SI{10}{\percent}. 
In terms of size, \(1000\) simulations were used for different sample sizes from the $\Gamma_{\text{SAR}}$ distribution, with varying values of $L$, and  $\mu=1$. 
In all cases, the nominal level was achieved. 
We assessed the test power using \(1000\) simulations for different sample sizes from the $G_I^0$ distribution, with  $\mu=1$, and $\alpha=-2$.
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.

@@

We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of \SI{10}{\meter} both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format.
The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels, and they contain mountainous areas, agricultural regions, water bodies, and urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(c).

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Coast of Jalisco, with $L=18$. (\\textbf{b}) Illinois-Region 1, with $L=36$. \\quad \\quad \\quad \\quad \\quad (\\textbf{c}) Illinois-Region 2, with $L=36$. ',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

knitr::include_graphics("../Figures/PNG/Mexico_512.png")
knitr::include_graphics("../Figures/PNG/lake_512.png")
knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")
```

The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows, as illustrated in Figures&nbsp;\ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.

The $p$-values obtained for each test are presented in Figures&nbsp;\ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue} and&nbsp;\ref{fig:Illinois_crops_pvalue}, respectively.

In Figures&nbsp;\ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level. 
Dark areas represent values below  $0.05$, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.

@@

Using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity.
It is justified that the dark areas of the maps based on the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ show coverage patterns similar to those reported for the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ map. 
This suggests that although CV-based tests may produce slightly less pronounced results than the entropy-based test, they still demonstrate a comparable ability to detect heterogeneity within SAR images.

@@

@@

This article provides a practical and theoretical answer to the following physical question: How to detect heterogeneity in SAR images, assuming that the SAR intensity follows the $\Gamma_{\text{SAR}}$ model.
To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two from the variation coefficient variants.
The performance of our proposals was evaluated using a Monte Carlo study. 
The results showed that they were conservative in estimating the probability of a type I error (false alarm rate) and the test power (probability of detection), which increases with sample size.
An application to three recent SAR images was performed. 
The results showed that the Shannon entropy-based test was more robust than the CV-based tests. 
In addition, all tests could recognize images with different textures and identify edges where the texture type changes.

>>>>

header-includes:
   - \usepackage[english]{babel}
   - \usepackage{bm,bbm}
   - \usepackage{mathrsfs}
   - \usepackage{siunitx}
   - \usepackage{graphicx}
   - \usepackage{url}
   - \usepackage[T1]{fontenc}
   - \usepackage{polski}
   - \usepackage{booktabs}
   - \usepackage{color}
   - \usepackage{xcolor}
   - \usepackage{amsmath}
   - \usepackage{multirow}
   - \usepackage{subcaption}
   # - \captionsetup[subfigure]{labelformat=parens, justification=centering}
   - \captionsetup[sub]{position=bottom,
        labelfont={bf, small, stretch=1.17},
        labelsep=space,
        textfont={small, stretch=1.5},
        aboveskip=1pt, 
        belowskip=1pt,
        singlelinecheck=off,
        justification=centering}   
   - \usepackage{placeins}

@@

In order to clarify the limit behavior when \(\alpha \to -\infty\) in Equation \eqref{E:E-GIO}, we show in Appendix&nbsp;\ref{app:1} that, for \(L=1\) and in the general case, the expression simplifies and the terms involving \(\alpha\) cancel out. Thus, the entropy of \(G_I^0\) converges to the entropy \(\Gamma_{\text{SAR}}\).

@@

```{r Plot_normality_qq, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="90%", fig.pos="H",  fig.cap="Normal Q--Q plots for  $n=121$. The dashed green lines in the Q--Q plots represent theoretical expected quantiles for a normal distribution. Variations in the scales of the axes reflect differences in the range of values across datasets.", fig.width=6, fig.height=5}

@@

After checking the data's normality, we examined the proposed test's abilities in terms of size (Type I error rate) and power (probability of correctly rejecting the null hypothesis when the alternative hypothesis is true).

Under \(\mathcal{H}_0\), the distribution of the test statistic is asymptotically normal.
Therefore, the \(p\) values are calculated as
\(2\Phi(-|\varepsilon|)\), where \(\Phi\) is the standard
Gaussian cumulative distribution function, and \(\varepsilon\) is the standardized test statistic given by:
\[
\varepsilon=\frac{\widetilde{H}_{\text{AO}}(\bm{Z})-\left[H_{\Gamma_{\text{SAR}}}(L)+\ln \widebar{\bm{Z}}\right]}{\widehat\sigma}.
\]

We conducted the test at nominal significance levels of \SI{1}{\percent}, \SI{5}{\percent}, and \SI{10}{\percent}. 
These levels represent the probability of rejecting the null hypothesis when it is actually true (Type I error rates). 
To verify that the test maintains these nominal levels, we performed $1000$ simulations under the null hypothesis ($\Gamma_{\text{SAR}}$ distribution), with different sample sizes and values of $L$, and $\mu=1$. In all cases, the observed Type I error rates were consistent with the nominal levels, indicating that the test maintains the specified significance levels.

We also evaluated the test's power by performing $1000$ simulations under the alternative hypothesis ($G_I^0$ distribution) with $\mu=1$ and $\alpha=-2$.
The power generally improves with increasing sample size and number of looks.
The results are shown in Table&nbsp;\ref{tab:table_size_power}.

@@

<!-- We evaluated the proposed test statistics using three SAR images: one of the coast of Jalisco, Mexico (with a spatial resolution of 20 m both along azimuth and range directions) and two of Illinois, USA (with a spatial resolution of \SI{10}{\meter} both along azimuth and range directions),  acquired by the Sentinel-1B satellite operating in C-band, with VV polarization and intensity format. -->
<!-- The first two images have a size of \(512 \times 512\) pixels, while the third has \(1024 \times 1024\) pixels, and they contain mountainous areas, agricultural regions, water bodies, and urban areas, as shown in  Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(d). -->

We evaluated the proposed test statistics using four SAR images: one of Rotterdam, Netherlands, acquired by the TerraSAR-X satellite with Single-look Slant-range Complex (SSC) and high-resolution Spotlight-mode (HS); another of the Coast of Jalisco, Mexico; and two of Illinois, USA, acquired by the Sentinel-1B in Ground Range Detected (GRD) format, with Extra Wide-swath mode (EW) and Strip Map mode (SM). Table&nbsp;\ref{tab:table_param} provides detailed parameters of the selected SAR images. They contain mountainous areas, agricultural regions, water bodies, and urban areas, as shown in Figures&nbsp;\ref{fig:real_SAR_Images_coe}(a)--(d).

The number of looks, $L$, was determined from the metadata in SNAP (Sentinel Application Platform), consisting of azimuth looks multiplied by range looks. This value also approximates the equivalent number of looks (ENL), calculated through the ratio of the squared sample mean to the sample variance in textureless areas.
\renewcommand{\arraystretch}{2}   
```{r parameters_sar, echo=FALSE, message=FALSE, warning=FALSE}

SAR_data <- data.frame(
  Site = c("Rotterdam", "Coast of Jalisco", "Illinois-Region 1", "Illinois-Region 2"),
  Mission = c("TerraSAR-X", "Sentinel-1B", "Sentinel-1B", "Sentinel-1B"),
  Mode = c("HS", "GRD EW", "GRD SM", "GRD SM"),
  Band = c("X", "C", "C", "C"),
  Polarization = c("HH", "VV", "VV", "VV"),
   Size = c("$512\\times512$", "$512\\times512$", "$512\\times512$", "$1024\\times1024$"),
  L = c(1, 18, 36, 36),
   Resol = c("$0.85/0.85$", "$40/40$", "$10/10$", "$10/10$"),
  Date = c("06-12-2018", "29-08-2021", "30-06-2020", "28-08-2021")
)

colnames(SAR_data) <- c("\\textbf{Site}", "\\textbf{Mission}", "\\textbf{Mode}", "\\textbf{Band}", "\\textbf{Polarization}", "\\textbf{Size}",  "$\\bm{L}$", "\\textbf{Resolution Rg/Az [m]} ", "\\textbf{Adquisition Date}")

SAR_data[] <- lapply(SAR_data, function(x) {
  if (is.numeric(x)) {
    if (all(x %% 1 == 0)) {
      formatted_numbers <- sprintf("$%d$", x)
    } else {
      formatted_numbers <- ifelse(x < 0, sprintf("$%.1f$", x), sprintf("$\\phantom{-}%.1f$", x))
    }
    return(formatted_numbers)
  } else {
    return(x)
  }
})

kable(SAR_data, caption = "Parameters of selected SAR images.",
      format = "latex",
      booktabs = TRUE,
      align = "ccccccccc",
      escape = FALSE,
      digits = 2,
      label = "table_param",
      centering = FALSE,
      table.envir = "table", position = "H") %>%
  row_spec(0, align = "c") %>%
  kable_styling(latex_options = "scale_down", font_size = 13) %>% 
  kable_styling(full_width = TRUE) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "1cm") %>%
  column_spec(5, width = "2cm") %>%
  column_spec(6, width = "2.5cm") %>%
  column_spec(7, width = "1cm") %>%
  column_spec(8, width = "3cm") %>%
  column_spec(9, width = "3cm")

Figures&nbsp;\ref{fig:optical_Images}(a)--(d) show the optical images obtained from Sentinel-2 L2A in true colors (composition of RGB channels) for the corresponding SAR images, with acquisition dates as follows: Rotterdam (20-12-2018), Coast of Jalisco (05-09-2021), Illinois-Region 1 (25-06-2020), and Illinois-Region 2 (01-08-2021). 
These optical images facilitate the interpretation of the results, making it easier to distinguish between homogeneous and heterogeneous regions.

```{r real_SAR_Images_coe, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='SAR images: (\\textbf{a}) Rotterdam, (\\textbf{b}) Coast of Jalisco, (\\textbf{c}) Illinois-Region 1, (\\textbf{d}) Illinois-Region 2.',  fig.subcap=c(' ', ' ',' ','' ), out.width = c("45mm","45mm", "45mm", "45mm"),  fig.ncol=2, fig.width = 20, fig.height = 10,fig.hspace=1.5}
knitr::include_graphics("../Figures/PNG/Rotterdam_1024.png")
knitr::include_graphics("../Figures/PNG/Mexico_512.png")
knitr::include_graphics("../Figures/PNG/lake_512.png")
knitr::include_graphics("../Figures/PNG/Illinois_1024_36L.png")

```{r optical_Images, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.align="center",fig.pos = 'H', fig.cap='Optical images: (\\textbf{a}) Rotterdam, (\\textbf{b}) Coast Jalisco, (\\textbf{c}) Illinois-Region 1, (\\textbf{d}) Illinois-Region 2.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm","45mm", "47mm", "42mm"),  fig.ncol=2, fig.width = 40, fig.height = 10}
knitr::include_graphics("../Figures/PNG/Rotterdam.png")
knitr::include_graphics("../Figures/PNG/Jalisco_o2.png")
knitr::include_graphics("../Figures/PNG/Sentinel2_Illinois_lake.png")
knitr::include_graphics("../Figures/PNG/Sentinel_2021_R2.png")
```

The three statistical tests are applied to the SAR images using $7\times 7$ local sliding windows (this window size is commonly used in practical scenarios, which strikes a balance between capturing detailed local information and ensuring a sufficient number of data points for solid analysis), as illustrated in Figures&nbsp;\ref{fig:test_Rotterdam}, \ref{fig:real_images_test_Mexico}, \ref{fig:test_lake} and&nbsp;\ref{fig:real_images_test_Illinois}.

The $p$-values obtained for each test are presented in Figures&nbsp;\ref{fig:Rotterdam_pvalue}, \ref{fig:Mexico_pvalue}, \ref{fig:lake_pvalue} and&nbsp;\ref{fig:Illinois_crops_pvalue}, respectively.

In Figures&nbsp;\ref{fig:Rotterdam_0.05}, \ref{fig:Mexico_crops_0.05}, \ref{fig:lake_0.05} and&nbsp;\ref{fig:Illinois_crops_0.05}, the maps of $p$-values composed of a linear gradient of black and white colors, represent the decisions at a \SI{5}{\percent} significance level. 
Dark areas represent values below  $0.05$, indicating evidence to reject the null hypothesis and suggesting heterogeneity in these regions. 
In contrast, values above 0.05 are represented as white areas, indicating no evidence to reject the fully-developed speckle hypothesis.

```{r test_Rotterdam, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results of applying the test statistics, Rotterdam: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b})  $T_\\text{CV}$, and (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c('', '', ''), out.width = c( "45mm","45mm", "45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}

knitr::include_graphics("../Figures/PNG/Entropy_AO_Rotterdam_1024.png")
knitr::include_graphics("../Figures/PNG/cv_Rotterdam.png")
knitr::include_graphics("../Figures/PNG/mnad_Rotterdam.png")
```

```{r Rotterdam_pvalue, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Map of $p$-values, Rotterdam: (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$. (\\textbf{b})  $T_\\text{CV}$. (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/H_pvalue_AO_Rotterdam_1024.png")
knitr::include_graphics("../Figures/PNG/cv_pvalues_Rotterdam.png")
knitr::include_graphics("../Figures/PNG/mnad_p_values_Rotterdam.png")

```{r Rotterdam_0.05, echo=FALSE, message=FALSE, warning=FALSE, fig.fullwidth = TRUE, out.width="100%",fig.pos = 'H', fig.cap='Results for a threshold of $0.05$ of the $p$-value, Rotterdam. (\\textbf{a}) $S_{\\widetilde{H}_{\\text{AO}}}(\\bm{Z}; L)$, (\\textbf{b}) $T_\\text{CV}$, and \\quad \\quad \\quad \\quad \\quad (\\textbf{c})   $T_{\\text{CV}_{\\text{MnAD}}}$.',  fig.subcap=c(' ', ' ',' ' ), out.width = c("45mm", "45mm","45mm"),  fig.ncol=3, fig.width = 20, fig.height = 10}
knitr::include_graphics("../Figures/PNG/H_005_AO_Rotterdam_1024.png")
knitr::include_graphics("../Figures/PNG/cv_005_pvalues_Rotterdam.png")
knitr::include_graphics("../Figures/PNG/mnad_005_Rotterdam.png")

@@

Using Shannon entropy is more meaningful than using the original and robust CV  to capture heterogeneity, particularly for Sentinel-1B images with a high number of looks.
It is justified that the dark areas of the maps based on the $T_\text{CV}$ and $T_{\text{CV}_{\text{MnAD}}}$ show coverage patterns similar to those reported for the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ map. 
This suggests that although CV-based tests may produce slightly less pronounced results than the entropy-based test, they still demonstrate a comparable ability to detect heterogeneity within SAR images.

@@

Conversely, when applying the same tests to a high-resolution TerraSAR-X image of Rotterdam, with a single look, the $S_{\widetilde{H}_{\text{AO}}}(\bm{Z}; L)$ test detected less heterogeneity compared to the CV-based tests. This indicates that the performance of the entropy test depends significantly on the number of looks, performing better with a higher number of looks as in the Sentinel-1B images.

@@

This article provides a practical and theoretical answer to the following physical question: How to detect heterogeneity in SAR images, assuming that the SAR intensity follows the $\Gamma_{\text{SAR}}$ model.
To this end, we proposed three novel hypothesis tests, one from the Shannon entropy and two from the variation coefficient variants.
The performance of our proposals was evaluated using a Monte Carlo study. 
The results showed that they were conservative in estimating the probability of a type I error (false alarm rate) and the test power (probability of detection), which increases with sample size.
An application to four recent SAR images was performed. 
The results showed that the Shannon entropy-based test was more robust than the CV-based tests for Sentinel-1B images.
For high-resolution images with a single look, such as the TerraSAR-X image, the classical CV test was more effective in detecting heterogeneous regions.
In addition, all tests could recognize images with different textures and identify edges where the texture type changes.

\appendixtitles{no} 
\appendixstart
\appendix
\section[\appendixname~\thesection]{}

## Limit Behavior of \(H_{G_I^0}\) as \(\alpha \to -\infty\) {#app:1}

To verify that \(H_{G_I^0}(\mu, \alpha, L)\) converges to \(H_{\Gamma_{\text{SAR}}}(L, \mu)\) as \(\alpha \to -\infty\),  we show that the additional terms in \(H_{G_I^0}\) cancel in the limit.

The Shannon entropy for the $G_I^0$ distribution is given by:
\begin{multline*}
H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu) - \ln \Gamma(L-\alpha) + (L-\alpha) \psi^{(0)}(L-\alpha) \\
- (1-\alpha) \psi^{(0)}(-\alpha) + \ln (-1-\alpha) + \ln \Gamma(-\alpha) - L.
\end{multline*}
We aim to show:
\[
\lim_{\alpha \to -\infty} H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu).
\]

The additional terms in \(H_{G_I^0}\) compared to \(H_{\Gamma_{\text{SAR}}}\) are:
\begin{align}
\label{E:lim1} \lim_{\alpha\to-\infty} \left[-\ln\Gamma(L-\alpha) + (L-\alpha) \psi^{(0)}(L-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)+\ln (-1-\alpha)+\ln\Gamma(-\alpha) \right]-L. 
 \end{align}

For \(L=1\), this becomes:
\begin{align}
\label{E:lim}
	 \lim_{\alpha\to-\infty} \bigg[\underbrace{-\ln\Gamma(1-\alpha) +\ln (-1-\alpha)+\ln\Gamma(-\alpha)}_{A} + \underbrace{(1-\alpha) \psi^{(0)}(1-\alpha)-(1-\alpha)\psi^{(0)}(-\alpha)}_{B}\bigg]-1.
 \end{align}

Simplifying \(A\) and \(B\):

\begin{align*}
	A=\ln\frac{(-1-\alpha)\cdot\Gamma(-\alpha)}{\Gamma(1-\alpha)}=\ln\frac{(-1-\alpha)\cdot\Gamma(-\alpha)}{-\alpha\Gamma(-\alpha)}=\ln\frac{-1-\alpha}{-\alpha}=\ln\left(1+\frac{1}{\alpha}\right).
\end{align*}

\begin{align*}
	B=(1-\alpha)\left[\psi^{(0)}(1-\alpha)-\psi^{(0)}(-\alpha)\right]&=(1-\alpha)\Bigg[\psi^{(0)}\underbrace{(1-\alpha-1)+\frac{1}{1-\alpha-1}}_{\text{Because}\, \psi^{(0)}(x+1)=\psi^{(0)}(x)+\frac{1}{x}}-\psi^{(0)}(-\alpha)\Bigg]\\
	&=(1-\alpha)\left[\psi^{(0)}(-\alpha)-\frac{1}{\alpha}-\psi^{(0)}(-\alpha)\right]\\
	&=-\frac{1}{\alpha}+1.
\end{align*}

Substituting the simplified expressions of \(A\) and \(B\) into \eqref{E:lim} and taking the limit, we obtain:
\begin{align*}
	 \underbrace{\lim_{\alpha\to-\infty}\ln\bigg(1+\frac{1}{\alpha}\bigg)}_{\text{approaches}\,\, 0}-\underbrace{\lim_{\alpha\to-\infty}\frac{1}{\alpha}}_{ \text{approaches}\,\, 0}+\lim_{\alpha\to-\infty}1-1=0.
 \end{align*}

 For the general case for $L>1$, we use Stirling's approximation for large \(z\):
 \[
\Gamma(z) \sim \sqrt{2\pi z} \left(\frac{z}{e}\right)^z,
\]
and  \[
\psi^{(0)}(z) \sim \ln(z) - \frac{1}{2z}. 
\]

Therefore, the terms of Equation \eqref{E:lim1} approximate to:
\[
-\ln\Gamma(L-\alpha) \sim -\frac{1}{2}\ln(2\pi(L-\alpha))-(L-\alpha)\ln(L-\alpha)+(L-\alpha).
\]
\[
(L-\alpha) \psi^{(0)}(L-\alpha) \sim (L-\alpha) \left[\ln(L-\alpha) - \frac{1}{2(L-\alpha)}\right] \sim (L-\alpha) \ln(L-\alpha) - \frac{1}{2}.
\]
\[
-(1-\alpha) \psi^{(0)}(-\alpha) \sim -(1-\alpha) \ln(-\alpha) - \frac{1-\alpha}{2\alpha}.
\]
\[\ln\Gamma(-\alpha)\sim \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha.\]

Then, substituting  these terms in \eqref{E:lim1} and applying limit we obtain:

\begin{multline*}
  \lim_{\alpha\to-\infty}\bigg[-\frac{1}{2}\ln(2\pi(L-\alpha))-L\ln(L-\alpha)+\alpha\ln(L-\alpha)+L-\alpha+ L\ln(L-\alpha) -\alpha\ln(L-\alpha)\\- \frac{1}{2}
-\ln(-\alpha)+\alpha\ln(-\alpha)- \frac{1-\alpha}{2\alpha}+ \ln (-1-\alpha)+ \frac{1}{2}\ln(-2\pi\alpha)-\alpha\ln(-\alpha)+\alpha\bigg]-L.
\end{multline*}

Simplifying each term:

\begin{multline*}
\lim_{\alpha\to-\infty}\bigg[-\frac{1}{2}\ln(2\pi(L-\alpha))+L- \frac{1}{2}-\ln(-\alpha)- \frac{1-\alpha}{2\alpha}
+ \ln (-(1+\alpha))+ \frac{1}{2}\ln(-2\pi\alpha)\bigg]-L.
\end{multline*}

\[
\lim_{\alpha\to-\infty}\bigg[\frac{1}{2}\ln\frac{-\alpha}{L-\alpha}+L- \frac{1}{2}+\frac{\alpha-1}{2\alpha}
+ \ln\frac{1+\alpha}{\alpha} \bigg]-L=\frac{1}{2}\ln(1)+L-\frac{1}{2}+\frac{1}{2}+\ln(1)-L=0.
\]

Therefore:

\[
\lim_{\alpha \to -\infty} H_{G_I^0}(\mu, \alpha, L) = H_{\Gamma_{\text{SAR}}}(L, \mu).
\]
